---
title: "waratah"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{waratah}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  dev = "ragg_png",
  collapse = TRUE,
  comment = "#>"
)
library(ggplot2, warn.conflicts = FALSE)
```

## Fonts

The NSW Government typeface is Public Sans.
Recommendations:

  - [Install the font](https://digitalnsw.github.io/public-sans/download/) on your computer. This package will attempt to register an embedded copy of the font so that it can be used even without installing the font first.
  - If possible you should use a graphics device that supports modern features such as `ragg::agg_png()`. These devices should be used by default by RStudio if {ragg} is installed.
  - If using HTML output (such as for interactive plots of tables), ensure that the document loads [Public Sans from Google Fonts](https://fonts.google.com/specimen/Public+Sans?preview.script=Latn) (see below).

<details><summary>Show font import code for HTML documents.</summary>
  Either add this to `<head>`:

  ```html
  <link href="https://fonts.googleapis.com/css2?family=Public+Sans:ital,wght@0,400;0,700;1,400&display=swap" rel="stylesheet">
  ```

  or add this to your CSS:

  ```css
  @import url('https://fonts.googleapis.com/css2?family=Public+Sans:ital,wght@0,400;0,700;1,400&display=swap');
  ```
</details>


## NSW Government logo

The logo included in PNG format:

```{r}
library(magick)
image_path <- system.file(
  "images",
  "nsw-gov-logo-primary.png",
  package = "waratah"
)
image_read(image_path)
```
