---
title: "Charts and graphs"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  dev = "ragg_png",
  collapse = TRUE,
  echo = FALSE,
  fig.width = 4,
  fig.height = 4,
  comment = "#>"
)
```

```{r setup}
library(waratah)
library(ggplot2, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
library(forcats)
library(reactable)

set_theme(theme_waratah())
```

```{r}
applications <- tibble::tribble(
  ~`Local government area` , ~`Applications assessed` ,
  "City of Sydney"         ,                      312 ,
  "Parramatta"             ,                      284 ,
  "Blacktown"              ,                      251 ,
  "Liverpool"              ,                      198 ,
  "Penrith"                ,                      176 ,
  "Camden"                 ,                      143
) |>
  mutate(
    `Local government area` = fct_reorder(
      `Local government area`,
      desc(`Applications assessed`)
    )
  )

support <- tibble::tribble(
  ~Quarter , ~Phone , ~Digital , ~`In person` ,
  "Q1"     ,   4200 ,     5800 ,         1100 ,
  "Q2"     ,   3900 ,     6400 ,          980 ,
  "Q3"     ,   3600 ,     7100 ,          890 ,
  "Q4"     ,   3200 ,     8200 ,          760
)
```

Examples derived from the NSW Design System [guidance on charts and graphs](https://designsystem.nsw.gov.au/docs/content/methods/charts-and-graphs.html).

## Comparison and ranking

<div class="container">
<div class="row">
<div class="col">

### Bar (vertical)

```{r}
ggplot(applications) +
  geom_col(aes(`Local government area`, `Applications assessed`)) +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_y_continuous(expand = expansion(mult = c(0, .2))) +
  theme(plot.margin = margin_part(l = 20)) +
  labs(
    title = "Development applications assessed",
    subtitle = "By local government area, January to March 2025",
    x = NULL,
    y = NULL
  )
```

**Summary**: City of Sydney and Parramatta assessed the highest number of applications in Q1 2025, together accounting for over a third of the total.

```{r}
reactable(applications, theme = reactable_theme())
```

**Source**: NSW Planning Portal. Last updated: March 2025.

</div>
<div class="col">

### Stacked bar

```{r}
support |>
  tidyr::pivot_longer(-Quarter) |>
  ggplot() +
  geom_col(aes(Quarter, value, fill = name)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  theme(legend.position = "bottom") +
  labs(
    title = "Support requests by contact type",
    subtitle = "Volume by channel, 2024-25 financial year",
    fill = NULL,
    x = NULL,
    y = NULL
  )
```

**Summary**: Digital contact grew steadily across all four quarters, while phone and in-person volumes declined. By Q4, digital accounted for more than two-thirds of all requests.

```{r}
reactable(support, theme = reactable_theme())
```

**Source**: Service NSW. Last updated: June 2025.

</div>
</div>
</div>
